SDR enhancement by clouds

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 11:12

```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
dailytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
dailyCE <- dailytrends[DATA == "ST_E_daily"]

@@

We computed the daily trend of the mean over irradiance of CE (Figure\
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.

By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of .....

Figures\ \ref{fig:CEmeanDaily}

## Trend

@@

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/P_energy-7.png")
```

@@

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/P_energy-6.png")
```

@@

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-5.png")
```

```{r echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-8.png")
```

>>>>

```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
dailytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
dailyCE <- dailytrends[DATA == "ST_E_daily"]
yearlytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]

@@

We computed the daily trend of the mean over irradiance of CE (Figure\ 
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.
The annual mean over irradiance is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
(Figure\ \ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean over irradiance per CE."}
knitr::include_graphics("../images/P_energy-7.png")
```

A better indicator of changes on the characteristic of CE would be the number of CE
occurrences and the total energy of the CE over irradiance. The annual number of CE
occurrences, shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
(Figure\ \ref{fig:P-energy-N}).

@@

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
knitr::include_graphics("../images/P_energy-6.png")
```
Subsequently, the annual energy observed during CE events shows a annual increase of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}).

@@

```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-5.png")
```

```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-8.png")
```

### 2024-03-19 article/article.tex
Commit 2024-03-19 11:12

We computed the daily trend of the mean over irradiance of CE (Figure\\
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by
implementing the function `arima' from the library `stats' of the R programming
language (R Core Team 2023). The trends were reported together with the \(2\sigma\) error.
We observe an increase of
\(0.216\pm 0.083\,W/m^2\)
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.

By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of \ldots..

Figures~\ref{fig:CEmeanDaily}

\hypertarget{trend}{%
\subsection{Trend}\label{trend}}

@@

\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-13}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-14}
\end{figure}

>>>>

We computed the daily trend of the mean over irradiance of CE (Figure~
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by
implementing the function `arima' from the library `stats' of the R programming
language (R Core Team 2023). The trends were reported together with the \(2\sigma\) error.
We observe an increase of
\(0.216\pm 0.083\,W/m^2\)
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.
The annual mean over irradiance is
\(0.23\pm 0.11\,W/m^2\)
(Figure~\ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

\caption{Trends of the mean over irradiance per CE.}\label{fig:P-energy-mean}
\end{figure}

A better indicator of changes on the characteristic of CE would be the number of CE
occurrences and the total energy of the CE over irradiance. The annual number of CE
occurrences, shows a steady increase of
\(122.2\pm 22.8\,/y\)
(Figure~\ref{fig:P-energy-N}).

@@

\caption{Trend of yearly CE number of occurancies.}\label{fig:P-energy-N}
\end{figure}

Subsequently, the annual energy observed during CE events shows a annual increase of
\(341.6\pm 73.1\,kJ/y\)
(Figure~\ref{fig:P-energy-sum}).

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:P-energy-sum}
\end{figure}

@@

\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:P-energy-median}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-10}
\end{figure}
